Hydra Battles and Cie

### 2021-07-29 doc/part-hydras.tex
converting chapter 2 to alectryon (continued)

\begin{Coqsrc}
Inductive S0 :  relation Hydrae :=
| S0_first : forall s, S0  (hcons head s) s
| S0_rest : forall  h s s',  S0  s s' ->
                             S0  (hcons h s) (hcons h s').

Inductive R1  :  Hydra -> Hydra -> Prop :=
| R1_intro : forall s s', S0 s s' -> R1 (node s) (node s').
\end{Coqsrc}

@@

\begin{Coqsrc}
Example Hy_1 : R1 Hy Hy'.
Proof. 
  split; right; right; left.
Qed.
\end{Coqsrc}

@@

\begin{Coqsrc}
Inductive S1 (n:nat)  : Hydrae -> Hydrae -> Prop :=
| S1_first : forall s h h' ,   R1 h h' -> 
                  S1 n (hcons h s) (hcons_mult h' (S n) s)
| S1_next : forall h s s',  S1 n s s' ->
                   S1 n (hcons h s) (hcons h s').
\end{Coqsrc}

@@

\begin{Coqsrc}
Inductive R2 (n:nat)  :  Hydra -> Hydra -> Prop :=
| R2_intro : forall s s', S1 n s s' -> R2 n (node s) (node s')
| R2_intro_2 : forall s s', S2 n s s' -> R2 n (node s) (node s')

with S2 (n:nat) :  Hydrae -> Hydrae -> Prop :=
|  S2_first : forall h h' s ,
               R2 n  h h'  -> 
               S2  n (hcons h s) (hcons h'  s)
|  S2_next  : forall h   r r',
               S2 n   r r' ->
               S2 n (hcons h r) (hcons h r').                  
\end{Coqsrc}

@@

\begin{Coqsrc}
Example R2_example:  R2 4 Hy' Hy''.
Proof.
    (** move to 2nd sub-hydra (0-based indices) *) R2_up 1. 
    (** move to first sub-hydra *)  R2_up 0.
    (** we're at distance 2 from the to-be-chopped-off head 
        let's go to the first daughter, 
        then chop-off the leftmost head *)  r2_d2  0 0. 
Qed.
\end{Coqsrc}

>>>>

\input{movies/snippets/Hydra_Definitions/S0Def}

\input{movies/snippets/Hydra_Definitions/R1Def}

@@

\input{movies/snippets/Hydra_Examples/Hy1}

@@

\input{movies/snippets/Hydra_Definitions/S1Def}

@@

\input{movies/snippets/Hydra_Definitions/R2Def}

@@

\input{movies/snippets/Hydra_Examples/R2Example}
